---
output: pdf_document
geometry: margin=0.5in
fontsize: 11pt
params:
  title: ''
title: "`r params$title`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width=12, fig.height=8, fig.asp = 0.8)
library(patchwork)
```

## Regular Plot
This is a test document showcasing the potential to render pdf's within a loop. This document will make use of the patchwork package to input interesting layouts. 
\vspace{10 mm}

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.align='center'}
p
```

## Function: horizontal_three_layout(plot1, plot2, plot3, plot_title = '', subtitle = '', caption = '', title_size = 18, title_font = 'mono', ...)

## Caption Size 9, Character Length must be 27 characters long for caption, title, and substitle
\vspace{10 mm}
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.align='center'}
horizontal_three_layout(p_hor_three, p_hor_three, p_hor_three,
                        plot_title = "titletitletitletitletitle",
                        subtitle = "titletitletitletitletitle",
                        caption = "titletitletitletitletitle")
```

## Function: horizontal_two_layout(plot1, plot2, plot_title = '', subtitle = '', caption = '', title_size = 18, title_font = 'mono', ...)

## Caption size 9, character Length must be 41 characters long for caption, title, subtitle
\vspace{10 mm}
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.align='center', fig.width=10}
horizontal_two_layout(p_hor_two, p_hor_two,
                        plot_title = "titletitletitletitletitle",
                        subtitle = "titletitletitletitletitle",
                        caption = "titletitletitletitletitle")
```

## Function: vertical_two_layout(plot1, plot2, plot_title = '', subtitle = '', caption = '', title_size = 18, title_font = 'mono', ...)
\vspace{10 mm}

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.align='center'}
vertical_two_layout(p_vert, p_vert,
                        plot_title = "titletitletitletitletitle",
                        subtitle = "titletitletitletitletitle",
                        caption = "titletitletitletitletitle")
```


## Function: horizontal_two_inset(plot1, plot2, position = 'top right', plot_title = '', subtitle = '', caption = '', title_size = 18, title_font = 'sans', ...)

## Size for caption, title, subtitle must be set at 7
\vspace{10 mm}

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.align='center'}
horizontal_two_inset(p_hor_two, p_blank,
                        plot_title = "titletitletitletitletitle",
                        subtitle = "titletitletitletitletitle",
                        caption = "titletitletitletitletitle")
```



## Function: horizontal_two_inset(plot1, plot2, position = 'top left', plot_title = '', subtitle = '', caption = '', title_size = 18, title_font = 'sans', ...)

## Size for caption, title, subtitle must be set at 7
\vspace{10 mm}

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.align='center'}
horizontal_two_inset(p_hor_two, p_blank, position = 'top left',
                        plot_title = "titletitletitletitletitle",
                        subtitle = "titletitletitletitletitle",
                        caption = "titletitletitletitletitle")
```




## Function: horizontal_two_inset(plot1, plot2, position = 'bottom left', plot_title = '', subtitle = '', caption = '', title_size = 18, title_font = 'sans', ...)

## Size for caption, title, subtitle must be set at 7
\vspace{10 mm}
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.align='center'}
horizontal_two_inset(p_hor_two, p_blank, position = 'bottom left',
                        plot_title = "titletitletitletitletitle",
                        subtitle = "titletitletitletitletitle",
                        caption = "titletitletitletitletitle")
```




## Function: horizontal_two_inset(plot1, plot2, position = 'bottom right', plot_title = '', subtitle = '', caption = '', title_size = 18, title_font = 'sans', ...)
## Size for caption, title, subtitle must be set at 7
\vspace{10 mm}

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.align='center'}
horizontal_two_inset(p_hor_two, p_blank, position = 'bottom right',
                        plot_title = "titletitletitletitletitle",
                        subtitle = "titletitletitletitletitle",
                        caption = "titletitletitletitletitle")
```


```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.align='center'}
horizontal_four_by_four(p_hor_small, p_hor_small, p_hor_small, p_hor_small,
                        plot_title = "titletitletitletitletitle",
                        subtitle = "titletitletitletitletitle",
                        caption = "titletitletitletitletitle")
```


```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.align='center'}
left_three_right_one(p_hor_small, p_hor_small, p_hor_small, p_hor_small,
                        plot_title = "titletitletitletitletitle",
                        subtitle = "titletitletitletitletitle",
                        caption = "titletitletitletitletitle")
```



```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.align='center'}
top_three_bottom_one(p_hor_small, p_hor_small, p_hor_small, p_hor_small,
                        plot_title = "titletitletitletitletitle",
                        subtitle = "titletitletitletitletitle",
                        caption = "titletitletitletitletitle")
```




















